Supplementary Materials

### 2021-08-20 analysis/index.Rmd
further development of manuscript

---
title: "Untitled"
author:
  - "Bjørn Peare Bartholdy"
  - Amanda G. Henry
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: no
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: default
  bookdown::html_document2: default
linestretch: 2.0 # double-spacing for review purposes
bibliography: paper/refs.bib
csl: paper/apa.csl
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "../figures")
library(tidyverse)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
## Compile refs.bib using rbbt package ##
file_paths <- here("analysis/paper", c("intro.Rmd", "matmet.Rmd", "disc.Rmd"))
cite_keys <- sapply(file_paths, rbbt::bbt_detect_citations) 
cite_keys <- unlist(cite_keys, use.names = FALSE)
rbbt::bbt_write_bib("./paper/refs.bib", keys = cite_keys, overwrite = T)
## end refs.bib ##
```

>>>>

---
title: "Untitled"
author:
  - "Bjørn Peare Bartholdy"
  - Amanda G. Henry
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    df_print: kable
    toc: no
    latex_engine: xelatex
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: default
  bookdown::html_document2:
    df_print: kable
    keep_md: true
linestretch: 2.0 # double-spacing for review purposes
bibliography: paper/refs.bib
csl: paper/apa.csl
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.path = "./figures/")
library(tidyverse)
library(broom)
library(here)
library(patchwork)
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
## Compile refs.bib using rbbt package ##
file_paths <- here("analysis/paper", c("intro.Rmd", "matmet.Rmd", "disc.Rmd"))
cite_keys <- sapply(file_paths, rbbt::bbt_detect_citations) 
cite_keys <- unlist(cite_keys, use.names = FALSE)
rbbt::bbt_write_bib("./paper/refs.bib", keys = cite_keys, overwrite = T)
## end refs.bib ##
```

### 2021-08-20 analysis/paper/disc.Rmd
further development of manuscript

@bjorckStarchProcessing1984; @henryCookingStarch2009]. 

@@

This means, that the dietary picture we obtain from starch granules extracted from 
dental calculus reflects a number of individual, dietary, and environmental (both
pre- and post-mortem environments) factors, and that this will likely be a

>>>>

@bjorckStarchProcessing1984; @henryCookingStarch2009]. Given the lack of $\alpha$-amylase 
activity detected in our model, hydrolysis is unlikely to be the main cause of our
reported low incorporation. More details on the absence of $\alpha$-amylase 
activity is discussed elsewhere<!--Bartholdy et al. in prep-->.

@@

What we can say, is that the dietary picture we obtain from starch granules extracted 
from dental calculus reflects a number of individual, dietary, and environmental 
(both pre- and post-mortem environments) factors, and that this will likely be a

### 2021-08-20 analysis/supplementary-materials/supp-mat.Rmd
further development of manuscript

---
title: Supplementary Materials
---

@@

>>>>

---
title: Supplementary Materials
output: 
  html_document:
    keep_md: true
    df_print: paged
---

```{r setup}
library(here)
library(tidyverse)
raw_data <- read_csv(here("analysis/data/raw_data/starch_counts.csv"))
```

@@

## Control samples

```{r}
raw_data %>%
  filter(treatment == "control") %>%
  select(!c(vol, portion_slide, s, m, l))
```

Only the total starch count was considered for control samples, as size was
deemed irrelevant.
